---
title       : Monkey Capital Management LLC
subtitle    : Can an Monkey beat the S&P 500 Index
author      : Rohit Padebettu
job         : 
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : night      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides

--- 
<style>
.title-slide {
  background-color: #FFFFFF; /* #EDE0CF; ; #CA9F9D*/
}
</style>
## Introduction

>* Hi, I am a portfolio manager from Monkey Capital Management LLC.

>* I have a ridiculously low IQ compared to most of you 
    - I think it maybe because I evolved earlier than you

>* But I do possess an amazing Algorithm for picking stocks

>* The problem is, I can only use it **once** to pick stocks

>* I can make up for that shortcoming though

>* *By working as hard as you want me to*

>* *For as long as you want me to*

>* *My Ambition:* **I really do want to beat the S&P 500 Index!**



--- bg:
## Methodology

>* I can pick upto 10 stocks using the **RANDOM Algo** (*developed by my Master*)

>* I can invest for upto 10 years or as low as 1 year

>* I can only equally weight stocks the Algo picks (*It is a quirk of my IQ*)

>* For now I have read up on the Dow 30 stocks (*I am confident that's enough*)

>* I work at 5 different speeds (*Master calls it Portfolio Rebalancing for some reason*)
    - Yearly
    - Quarterly
    - Monthly
    - Weekly
    - Daily

>* I benchmark myself against my "Lazy" Buy & Hold brother and also the "Evil" S&P500 Index


--- bg:lightgoldenrodyellow
## Portfolio Analytics
I make some cool charts and tables available to you to assess my performance
```{r,echo=F,fig.align='center',warning=FALSE}
suppressWarnings(source('../Script.R'))
```

```{r,echo=F,fig.align ='center',fig.width=12,fig.height=6}
charts.PerformanceSummary(plot_data,colorset=rainbow6equal,lwd=2)
```

--- bg:lightgoldenrodyellow
## Portfolio Value
```{r,echo=F,fig.align ='center',fig.width=12,fig.height=7}
chartSeries(portfolio_rebal$wealthindex*100,name = "Value of Portfolio")
```


---
## Performance Breakdown
```{r,echo=F, results='asis'}
perf_return = xts()
perf_return$rebal<-monthlyReturn(portfolio_rebal$wealthindex,type = 'arithmetic',leading = TRUE)
perf_return$bh<-monthlyReturn(portfolio_buyhold$wealthindex,type = 'arithmetic',leading = TRUE)
perf_return$bmk<-monthlyReturn(benchmark_portfolio$wealthindex,type = 'arithmetic',leading = TRUE)
names(perf_return)<-c("Rebalanced Portfolio","BuyHold Portfolio","Benchmark")
suppressPackageStartupMessages(require(xtable))
print(xtable(t(table.CalendarReturns(perf_return))),type='html',)
```



